Triangulating iconicity: Coding analysis

### 2022-01-31 paper_coding_2_analysis.Rmd
started making shiny app to explore data

# write this dataset as the fullest dataset
write.csv(d,file="data/ideophones_coded_guessed_rated.csv")
write_xlsx(d,path="data/ideophones_coded_guessed_rated.xlsx")

>>>>

# write this dataset as the fullest dataset
write.csv(d,file="data/ideophones_coded_guessed_rated.csv",fileEncoding = "UTF-8")
write_xlsx(d,path="data/ideophones_coded_guessed_rated.xlsx")
